Selective electroporation of the viral envelope via optimal control of transmembrane potential

### 2021-06-17 documents/pure_electroporation.tex
Hampath math notes

The most obvious difference is scale. All other properties of the system being equal, the standard Schwan equation for transmembrane voltage implies that the steady-state DC voltage is proportional to the size of the particle. In the case of a 100 nm virus, this would 400x difference, which is reflected precisely in the steady state numerical simulations that follow.

@@

	This transposition was only detected late in the project, and so some documentation may still contain the incorrect coefficients. Beware.

@@

This bears considerable similarity to e.g. radar waveform design and compressed sensing; problems of coherent control of quantum systems. In many cases, the optimal control is equal to the transfer function

@@

single input, multiple output

underactuated robotics, simultaneous stabilization\cite{results1984}\cite{Simultaneous2005}

@@

For PSOPT, a further modification was needed, as the library does not support the derivative of the control; the second derivative was used as the control, and input into a differential-algebraic equation form.

@@

Both PSOPT and GEKKO's APMonitor backend use the famous ipopt solver. A number of linear solvers can be used. LANL's Tasseff's integration with the SPRAL solver, reportedly faster on large problems, was

@@

\subsection*{Limitations and next steps}

@@

\subsection{Software used and evaluated:}

@@

\subsection{Recommended reading}

>>>>

The most obvious difference is scale. All other properties of the system being equal, the standard Schwan equation for transmembrane voltage, $\Delta \phi = (3/2) E R \cos(\theta)$ implies that the steady-state DC voltage is proportional to the size of the particle. In the case of a 100 nm virus, this would 400x difference, which is reflected precisely in the steady state numerical simulations that follow.

@@

	This minor transposition was only detected late in the project, and so some documentation may still contain the incorrect coefficients. Beware.

@@

This bears considerable similarity to e.g. radar waveform design and compressed sensing; problems of coherent control of quantum systems, single input multiple output underactuated robotics, simultaneous stabilization\cite{results1984}\cite{Simultaneous2005}.

In many cases, the optimal (minimum-energy) control is equal to the transfer function

@@

@@

For PSOPT, a further modification was needed, as the library does not appear to natively support the second derivative of the control; the second derivative was used as the control, and input into a differential-algebraic equation form.

@@

Both PSOPT and GEKKO's APMonitor backend use the famous ipopt solver. A number of linear solvers can be used. LANL's Tasseff's integration with the SPRAL solver, reportedly faster on large problems, was . HSL libraries ma57 and ma97 were used.

@@

\section*{Sensitivity analysis}

\section*{Limitations and next steps}

@@

sensitivity analysis

\subsection*{Software used and evaluated:}

@@

\subsection*{Recommended reading}
